---
title: "Tooth"
author: "Isa Baghirov"
date: "01 02 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of Tooth Growth data in R



```{r}
library(ggplot2)
library(datasets)
str(ToothGrowth)
summary(ToothGrowth)
```
```{r}
qplot(dose ,len ,data = ToothGrowth, 
      col = supp, 
      main = "Length Growth by supplement type and dosage", 
      xlab = "Dosage", 
      ylab = "Length Growth")
```
```{r}
qplot(supp, len, data = ToothGrowth, 
      facets = ~dose, 
      main = "Tooth growth of guinea pigs by supplement type and dosage (mg)", 
      xlab = "Supplement type", 
      ylab = "Tooth length") + 
        geom_boxplot(aes(fill = supp))
```
The null hypothesis is VC supplementary growth is more than OJ supplementary growth.
```{r}
VC <- ToothGrowth$len[ToothGrowth$supp == "VC"]
OJ<- ToothGrowth$len[ToothGrowth$supp == "OJ"]
t.test(VC, OJ, 
       alternative = "greater", # testing hypothesis if Vc is greater than VC
       paired = FALSE, # the data point are not paired with each other
       var.equal = FALSE, # the variances are not equal
       conf.level = 0.98) # a 98% confidence interval is taken as the default if nothing else is defined
```
The P-value is 0.9697, so null hypothesis is true.

The null hypothesis is that tooth growth for 0.5 is less than 1.
```{r}
d0.5 <- ToothGrowth$len[ToothGrowth$dose == "0.5"]
d1   <- ToothGrowth$len[ToothGrowth$dose == "1"]
d2   <- ToothGrowth$len[ToothGrowth$dose == "2"]
t.test(d0.5, d1, alternative = "greater", # is the alternative that d1 has a greater mean than d0.5 
       paired = FALSE,
       var.equal = FALSE,
       conf.level = 0.98)
```

The P-Value is 1, so the null hypothesis is true.

The null hypothesis is that for d1 growth is less than for d2
```{r}
t.test(d1, d2, 
       alternative = "greater", # is the alternative that dose_1 has a greater mean than dose_2
       paired = FALSE, 
       var.equal = FALSE, 
       conf.level = 0.98)
```
The P-value is also 1, so the null hypothesis is also true